Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-10 paper.tex
minor

\begin{table*}
\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.} JAMIE, PLEASE CHECK VALUES IN RED [rs]} Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.} 
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{\rev{$\eta=10^{-4}$}}& \multicolumn{2}{c}{\rev{$\eta=10^{-3}$}} \\
&
Anisotropic &
Isotropic &
Anisotropic &
Isotropic \\
\midrule
Theoretical average ideal linear growth rate of flute $\gamma$
& 0.88 
& \rev{0.88} 
& 1.73 
& \rev{1.73} \\
Observed growth rate of flute $\gamma$
& 0.69 
& \rev{--} 
& 1.06 
& \rev{1.06}\\
Observed growth rate of kink $\lambda$
& 2.55 
& \rev{2.97} 
& 0.15 
& \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{1.63}\\
\midrule
\rev{Predicted axial wave number $k_{\text{flute}}$}
& 23.74
& 23.52
& 17.15
& 17.60\\
Observed axial wave number $k_{\text{flute}}$
& \rev{22.67 \pm 1}
& \rev{22.71 \pm 1}
& \rev{16.12 \pm 0.4}
& \rev{16.25 \pm 0.4}\\
Observed axial wave number $k_{\text{kink}}$
& \rev{4.57}
& \rev{4.41}
& \rev{3.44}
& \rev{3.49}\\
\midrule
\rev{Cumulative viscous heat at $t=50$}
& $1.64 \times 10^{-2}$ 
& 1.28 
& $2.89 \times 10^{-3}$ 
& 0.370 \\
\rev{Cumulative Ohmic heat at $t=50$}
& 3.06 
& 2.75 
& 6.54 
& 6.27 \\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}

>>>>

\begin{table*}
\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.} JAMIE, PLEASE CHECK VALUES IN RED [rs]} Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.} 
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{\rev{$\eta=10^{-4}$}}& \multicolumn{2}{c}{\rev{$\eta=10^{-3}$}} \\
&
Anisotropic &
Isotropic &
Anisotropic &
Isotropic \\
\midrule
Theoretical average ideal linear growth rate of flute $\gamma$
& 0.88 
& \rev{0.88} 
& 1.73 
& \rev{1.73} \\
Observed growth rate of flute $\gamma$
& 0.69 
& \rev{--} 
& 1.06 
& \rev{1.06}\\
Observed growth rate of kink $\lambda$
& 2.55 
& \rev{2.97} 
& 0.15 
& \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{1.63}\\
\midrule
\rev{Predicted axial wave number $k_{\text{flute}}$}
& 23.74
& 23.52
& 17.15
& 17.60\\
Observed axial wave number $k_{\text{flute}}$
& \rev{$22.67 \pm 1$}
& \rev{$22.71 \pm 1$}
& \rev{$16.12 \pm 0.4$}
& \rev{$16.25 \pm 0.4$}\\
Observed axial wave number $k_{\text{kink}}$
& \rev{4.57}
& \rev{4.41}
& \rev{3.44}
& \rev{3.49}\\
\midrule
\rev{Cumulative viscous heat at $t=50$}
& $1.64 \times 10^{-2}$ 
& 1.28 
& $2.89 \times 10^{-3}$ 
& 0.370 \\
\rev{Cumulative Ohmic heat at $t=50$}
& 3.06 
& 2.75 
& 6.54 
& 6.27 \\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}
